Molecular alignment on graphene surface determines tansport properties of graphene/organic semiconductor transistors

### 2020-04-08 manuscript.tex
added most of Egon's corrections, only two headings (morphology and transport)

\subsection{Transconductance of clean graphene}
\label{sec:clean}

The understanding of morphological properties of the OS layer and its growth mode is important for the interpretation of the charge transport data presented in the following.
  In organic semiconductors charge transport proceeds by hopping in a manifold of localized molecular electronic states and is thus strongly dependent on the relative orientation of the molecules and the degree of positional disorder in the layers.
  On graphene instead, charge transport is characterized by Bloch-like extended states, which reside, in the case of a single-layer graphene in a relatively disorder-free environment.
  The effect of PDI8-CN2 layers on charge transport through graphene was studied by measuring the transfer characteristics of GFETs with different amounts of PDI8-CN2 grown on graphene channel.
 Typical evolution of transconductance current for clean graphene and two different coverages is illustrated in Figure \ref{fig:3}, where we show the results of measurements (symbols) obtained on GFETs comprising clean single-layer (brown curve), GFET with PDI8-CN2 deposition of 1 minute and PDI8-CN2 (blue curve) and with deposition of 3 minutes (green curve).
  Only a forward gate sweep (from $V_g<0$ to $V_g>0$) data are shown.
 A minimal hysteresis was observed (See Supplementary information) indicating the density of traps is less than \textbf{XX cm$^{-2}$ - we can calculate this from the dirac shift due to hysteresis} that would originate from the structural and/or chemical defects in the layers.
\TODO{Also shown are the results of fitting to a model function (black dashed curves) explained below}.

\begin{figure}[htb]
  \centering
   \includegraphics[width=0.9\textwidth]{./Figures/fig3}  
  \caption{Transconductance measurements of a graphene field-effect transistor at different PDI8-CN2 coverages of graphene.
 Brown curve corresponds to clean graphene, blue curve corresponds to a coverage of 0.7 obtained by the PDI8-CN2 deposition of 1 minute.
 The green curve corresponds to the coverage obtained by PDI8-CN2 deposition of 4 minutes.
 The corresponding morphologies are shown in Figures 1 and 2, respectively. 
 \TODO{Dashed curves represent a model explained in the text}. 
 }
  \label{fig:3}
\end{figure}

We observe transfer characteristics of GFET comprising clean graphene exhibiting charge-neutrality point (CNP) at back-gate voltage of 8 V.
  The position of CNP relative to the Dirac point (0 V) is consistent with $p$-type doping of graphene caused by the trap states on SiO$_{2}$ surface and chemical redox reaction occurring at the graphene/SiO$_{2}$ interface\cite{feng-2014,peng-2017,lafkioti-2010}.
  In addition to the shift of the CNP we observe also a strong reduction in the slope of the transfer curve occurring at about 1 V, leading to a plateau of the drain current.

@@

\subsection{Transconductance - submonolayer coverage}
\label{sec:first}

@@

\subsection{Transconductance of the complete PDI8-CN2 layer}
\label{sec:complete}

@@

\subsection{Model}
\label{sec:model}
\TODO{The transconductance models, shown with a dashed line in Figure \ref{fig:4}},
  were devised under the following assumptions.
  The drain current was  calculated as:
  \begin{equation}
    \label{eq:2}
    I_{D}=\frac{W}{L}\mu n e(V_{D}- 2I_{D}R_{C})
  \end{equation}
  \noindent With $W$ and $L$ channel width and length respectively, $R_{C}$ the resistance of both metallic contacts, $\mu$ charge carrier mobility and $n$ their concentration.
   Given by:
  \begin{equation}
    \label{eq:3}
    n=\sqrt{n_{o}^{2}+n^{2}(V_{g})}
  \end{equation}
 $n_o$ represents a carrier concentration induced by impurities\cite{adam-2007}.
 While $n(V_{g})$ represents surface density of charge in graphene ($n$), which depends on the gate voltage and effective capacitance of the graphene/dielectric/bottom gate electrode. 
 Effective capacitance can be modelled as a serial connection of the quantum capacitance, given by $C_{\mu} = e^2dn/dE_F$, which results from the Fermi energy ($E_F$) shift in graphene, 
 and the electrostatic geometrical (displacement) capacitance between the graphene layer and the gate electrode, given by $C_{ox}=(\epsilon_0\epsilon)/d_{ox}$\cite{sze-2006,chhikara-2014,das-2008}.
 $C_{\mu}$ is calculated from the dependence of the Fermi energy on the charge density and it was experimentally observed  to be larger than $C_{\mu} \geq 8 \times10^{-7}$ F cm$^{-2}$ \cite{xia_2009}.
 However, $C_{ox}=1.2\times10^{-12}$ F cm$^{-2}$, with dielectric constant of SiO$_{2}$  $\epsilon \approx 4$ and $d_{ox}=$285 nm, which is considerably smaller than $C_{\mu}$.
 Its contribution to the effective capacitance is insignificant.
 Hence, the quantum capacitance in the case of bottom gate contact may therefore be safely neglected\cite{das-2008}. 
 Therefore, the $V_{g}$-modulated carrier concentration in graphene is given by
 \begin{equation}
   \label{eq:4}
   n(V_{g})= \frac{C_{ox}}{e}(V_{g}- V_{CNP})
 \end{equation}
 \noindent With $V_{CNP}$ the gate voltage of the charge-neutrality point\cite{xia-2010}.
 The total resistance plots were calculated from the transconductance ($R=V_{G}/I_{DS}$) and are presented in Figure \ref{fig:4}.
 The total resistance of the GFET is the resistance of the graphene channel plus the resistance of the contacts.
 The relation of $R$ was obtained from (\ref{eq:2}-\ref{eq:4}):	
 \begin{equation}
	 \label{eq:5}
     R_{tot} = \frac{V_{D}}{I_{D}} = \frac{L}{W\mu e\sqrt{n_{0}^{2}+n^{2}(V_{g})}} +2 R_{c}
 \end{equation}
 \noindent The results of the least-square fitting of (\ref{eq:5}) to measurements are shown by black solid lines in Figure \ref{fig:4}. The fitting parameters were $R_{c}$, $\mu$, $n_0$ and $n(V_{CNP})$.
 Their corresponding values are summarised in Table \ref{tab:1}.

\begin{figure}[htb]
  \centering
   \includegraphics[width=0.9\textwidth]{./Figures/fig4}  
  \caption{Resistance calculated from the data presented in Figure {\ref{fig:4}} (symbols).
 Solid lines represent least-squares fits based on the Equation \ref{eq:5}.
}
  \label{fig:4}
\end{figure}

@@

\subsection{Interpretation of the Fitting Results}
\label{sec:interp}

>>>>

 \subsection{Transport properties}
\label{sec:tran}

The understanding of morphological properties of the OS layer and its growth mode is important for the interpretation of the charge transport data presented in the following.
  In organic semiconductors charge transport proceeds by hopping in a manifold of localized molecular electronic states and is thus strongly dependent on the relative orientation of the molecules and the degree of positional disorder in the layers.
  On graphene instead, charge transport is characterized by Bloch-like extended states, which reside, in the case of a single-layer graphene in a relatively disorder-free environment.
  The effect of PDI8-CN2 layers on charge transport through graphene was studied by measuring the transfer characteristics of GFETs with different amounts of PDI8-CN2 grown on graphene channel.
 Typical evolution of transconductance current for clean graphene and two different coverages is illustrated in Figure \ref{fig:3}, where we show the results of measurements (symbols) obtained on GFETs comprising clean single-layer (brown curve), GFET with PDI8-CN2 coverage of 1 minute and PDI8-CN2 (blue curve) and with coverage of 3 minutes (green curve).
 Only a forward gate sweep (from $V_g<0$ to $V_g>0$) data are shown.
 A minimal hysteresis was observed  indicating the  a relatively low density of traps that would originate from the structural and/or chemical defects in the layers.

\begin{figure}[htb]
  \centering
   \includegraphics[width=0.9\textwidth]{./Figures/fig3}  
  \caption{Transconductance measurements of a graphene field-effect transistor at different PDI8-CN2 coverages of graphene.
 Brown curve corresponds to clean graphene, blue curve corresponds to a coverage of 0.7 obtained by the PDI8-CN2 deposition of 1 minute.
 The green curve corresponds to the coverage obtained by PDI8-CN2 deposition of 4 minutes.
 The corresponding morphologies are shown in Figures 1 and 2, respectively. 
 }
  \label{fig:3}
\end{figure}

We observe transfer characteristics of a GFET comprising clean graphene exhibiting charge-neutrality point (CNP) at back-gate voltage of 8 V.
  The position of CNP relative to the Dirac point (0 V) is consistent with $p$-type doping of graphene caused by the trap states on SiO$_{2}$ surface and chemical redox reaction occurring at the graphene/SiO$_{2}$ interface\cite{feng-2014,peng-2017,lafkioti-2010}.
  In addition to the shift of the CNP we observe also a strong reduction in the slope of the transfer curve occurring at about 1 V, leading to a plateau of the drain current.

@@

@@

@@

%%model

The resistance ($R=V_{G}/I_{DS}$) plots calculated from the data used to plot Figure \ref{fig:3} are shown in Figure \ref{fig:4} where we also show the results of a least-square fitting of the data (symbols) to a model function explained in the following.
In the outset we note that the drain current was calculated as:
  \begin{equation}
    \label{eq:2}
    I_{D}=\frac{W}{L}\mu n e(V_{D}- 2I_{D}R_{C})
  \end{equation}
  \noindent With $W$ and $L$ channel width and length respectively, $R_{C}$ the resistance of both metallic contacts, $\mu$ charge carrier mobility and $n$ their concentration.
   Given by:
  \begin{equation}
    \label{eq:3}
    n=\sqrt{n_{o}^{2}+n^{2}(V_{g})}
  \end{equation}
 Here $n_o$ represents a carrier concentration induced by charged impurities residing within the SiO$_{2}$ and arise from the reactions on its surface\cite{adam-2007}.
 $n(V_{g})$ represents surface density of charge in graphene ($n$), which depends on the gate voltage and the graphene/bottom gate capacitance.
The latter can be considered as sum of  the quantum capacitance -- dependent on the position of the  Fermi level ($E_F$)  in  graphene, 
 and the electrostatic  capacitance between the graphene layer and the gate electrode, given by $C_{ox}=(\epsilon_0\epsilon)/d_{ox}$\cite{sze-2006}.
 For the thickness of the SiO$_{2}$ $d_{ox}=$285 nm and its dielectric constant  $\epsilon \approx 4$,  $C_{ox}=1.2\times10^{-12}$ F cm$^{-2}$.
 The quantum capacitance has been shown to be on the order of $ \geq 8 \times10^{-7}$ F cm$^{-2}$ \cite{xia_2009}, and can therefore be ignored in our case\cite{das-2008}. 
 Therefore, the $V_{g}$-modulated carrier concentration in graphene is given by
 \begin{equation}
   \label{eq:4}
   n(V_{g})= \frac{C_{ox}}{e}(V_{g}- V_{CNP})
 \end{equation}
 \noindent With $V_{CNP}$ the gate voltage of CNP\cite{xia-2010}.
 The total resistance $R$ of the structure is the resistance of the  channel plus the resistance of the contacts and can be  obtained from (\ref{eq:2}-\ref{eq:4}):	
 \begin{equation}
	 \label{eq:5}
     R_{tot} = \frac{V_{D}}{I_{D}} = \frac{L}{W\mu e\sqrt{n_{0}^{2}+n^{2}(V_{g})}} +2 R_{C}
 \end{equation}
 \noindent The results of the least-square fitting of (\ref{eq:5}) to measurements are shown by black solid lines in Figure \ref{fig:4}. The fitting parameters were $R_{C}$, $\mu$, $n_0$ and $n(V_{CNP})$.
 Their  values for the three cases considered are summarised in Table \ref{tab:1}.

\begin{figure}[htb]
  \centering
   \includegraphics[width=0.9\textwidth]{./Figures/fig4}  
  \caption{Resistance calculated from the data presented in Figure {\ref{fig:3}} (symbols).
 Solid lines represent least-squares fits based on the Equation \ref{eq:5}.
}
  \label{fig:4}
\end{figure}

@@
